Seagrass mapping and monitoring along the coasts of Crete, Greece

### 2011-01-14 MScDiplom_Lemenkova.tex
added statistics in Gretle, R

\documentclass[10pt, a4paper]{article}
\usepackage{color}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{calc}
\usepackage{longtable}
\usepackage[svgnames,table]{xcolor}
%\usepackage[table]{xcolor}
\usepackage{paralist}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{fancyheadings}
\topmargin = 1pt
\headheight=10mm
\headsep=7pt
%\ensuremath
\usepackage{lastpage}
\usepackage{float}
\usepackage{subfig}
\usepackage{caption}
\usepackage{appendix}
\captionsetup{margin=10pt,font=small,labelfont=bf}
\usepackage{wrapfig}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\setcounter{tocdepth}{4}
\parindent 0pt
%\floatstyle{boxed} 
\restylefloat{figure}
\usepackage[a4paper=true, ]{hyperref}

@@

\textbf{Software and utilities used in the current work}:\\
\begin{itemize}
\item \href{http://www.esri.com/software/arcgis/index.html}{ArcGIS 10.0}: mapping, data integration and spatial analysis
\item \href{http://www.erdas.com/products/ERDASIMAGINE/ERDASIMAGINE/Details.aspx}{Erdas Imagine}: imagery processing and classification
\item WASI Water Color Simulator, for modelling optical water properties under changing environment
\item \href{http://welcome.hp.com/country/us/en/prodserv/handheld.html}{iPAQ} and GPS for data capture during the fieldwork
\item \href{http://www.bibtex.org/de/}{BibTeX}, for management of bibliography and reference database
\item \href{http://www.latex-project.org/}{\LaTeX}, for document typesetting, formatting and performing pdf output
\item \href{http://www.python.org/}{Python language}, for writing auxiliary scripts (e.g. raw data interpolation)
\item \href{http://www.gnuplot.info/}{Gnuplot} for plotting graphs
\item \href{http://www.openoffice.org/}{Open Office} : document typesetting, data preprocessing and preliminary statistical evalution
\item \href{http://calc2latex.sourceforge.net/}{Calc2LaTeX} : converting spreadsheets into \LaTeX environment
\item \href{http://www.spss.com/}{SPSS (PASW Statistics 18)} : statistical data edition and analysis 
\end{itemize}
\pagebreak

@@

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.25]{GNU-09.jpg}
\caption{Spectral reflectance of seawater with sediments. Bezier interpolation. Mean value is shown by the vertical impulses linestyle (GNUplot)­}
\label{fig:52}
\end{center}
\end{figure}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.25]{GNU-10.jpg}
\caption{Spectral reflectance of the seawater without sediments. Interpolation graph. GNUplot display­}
\label{fig:53}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.25]{GNU-11.jpg}
\caption{Spectral reflectance of P.oceanica. Measurement series 25-50. GNUplot display­}
\label{fig:54}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.25]{GNU-12.jpg}
\caption{RS reflectance of P.oceanica. Series 1-25. Shown midspread of the statistical quartiles Q1 and Q3 (vertical dashes) and
mean value within the range.­}
\label{fig:55}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.4]{GNU-14.jpg}
\caption{Multiplot of spectral reflectance of P.oceanica. Series 126-150. Shown midspread of the statistical quartiles Q1 and Q3 (vertical dashes) and
mean value within the range (red bold dots). GNUplot visualization­}
\label{fig:56}
\end{center}
\end{figure}
\pagebreak

\begin{table}[htbp]
\rowcolors{1}{Ivory}{GhostWhite}
\caption{Initial Cluster Centers: results of the \textit{K-means} analysis of the measurement set 201-236 of the spectral reflectance of \textbf{P.oceanica} (15.X.). SPSS}
\label{tab:13}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline\hline
& \multicolumn{2}{|c|}{Cluster} &  & \multicolumn{2}{|c|}{Cluster}\\
%\cline{2,3,5,6}
 & 1 & 2 &  & 1 & 2 \\ \hline\hline
V2 &	.353010 &	.000644 &	V16 &	.240091 &	.000374 \\ \hline
V3 &	 .271519 &	.000394 &	V17 &	.270306 &	.000435 \\ \hline
V4 &	.273594 &	.000644 &	V18 &	.196188 &	.000211 \\ \hline
V5 &	.406525 &	.000527 &	V19 &	.301486 &	.000370 \\ \hline
V6 &	.344973 &	.000509 &	V20 &	.178575 &	.000328 \\ \hline
V7 &	.395117 &	.000646 &	V21 &	.231708 &	.000440 \\ \hline
V8 &	.254642 &	.000352 &	V22 &	.186493 &	.000365 \\ \hline
V9 &	.288881 &	.000267 &	V23 &	.261761 &	.000418 \\ \hline
V10 &	.191850 &	.000255 &	V24 &	.282032 &	.000264 \\ \hline
V11 &	.249462 &	.000323 &	V25 &	.190709 &	.000375 \\ \hline
V12 &	.209622 &	.000414 &	V26 &	.177432 &	.000206 \\ \hline
V13 &	.218312 &	.000206 &	V27 &	.195104 &	.000268 \\ \hline
V14 &	.177432 &	.000268 &	V28 &	.256630 &	.000386 \\ \hline
V15 &	.184836 &	.000223 &	V29 &	.283744 &	.000436 \\ \hline
	 &	 &	 &		V30 &	.406525 &	.000646 \\ \hline
\end{tabular}
\end{center}
\label{fig:5}
\end{table}

>>>>

\documentclass[10pt, a4paper]{article}
\usepackage{color}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{calc}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage[svgnames,table]{xcolor}
%\usepackage[table]{xcolor}
\usepackage{paralist}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{fancyheadings}
\topmargin = 1pt
\headheight=10mm
\headsep=7pt
%\ensuremath
\usepackage{lastpage}
\usepackage{float}
\usepackage{subfig}
\usepackage{caption}
\usepackage{appendix}
\captionsetup{margin=10pt,font=small,labelfont=bf}
\usepackage{wrapfig}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\setcounter{tocdepth}{4}
\parindent 0pt
%\floatstyle{boxed} 
\restylefloat{figure}
\usepackage[a4paper=true, ]{hyperref}

@@

\textbf{Software and utilities used in the current work}:\\
\begin{itemize}
\item \href{http://www.esri.com/software/arcgis/index.html}{ArcGIS 10.0}: mapping, data integration and spatial analysis
\item \href{http://www.erdas.com/products/ERDASIMAGINE/ERDASIMAGINE/Details.aspx}{Erdas Imagine}: imagery processing and classification
\item WASI Water Color Simulator, for modelling optical water properties under changing environment
\item \href{http://welcome.hp.com/country/us/en/prodserv/handheld.html}{iPAQ} and GPS for data capture during the fieldwork
\item \href{http://www.bibtex.org/de/}{BibTeX}, for management of bibliography and reference database
\item \href{http://www.latex-project.org/}{\LaTeX}, for document typesetting, formatting and performing pdf output
\item \href{http://www.python.org/}{Python language}, for writing auxiliary scripts (e.g. raw data interpolation)
\item \href{http://www.gnuplot.info/}{Gnuplot} for plotting graphs
\item \href{http://www.openoffice.org/}{Open Office} : document typesetting, data preprocessing and preliminary statistical evalution
\item \href{http://calc2latex.sourceforge.net/}{Calc2LaTeX} : converting spreadsheets into \LaTeX environment
\item \href{http://www.spss.com/}{SPSS (PASW Statistics 18)} : statistical data edition and analysis 
\item \href{http://gretl.sourceforge.net/}{Gretl: Gnu Regression, Econometrics and Time-series Library} for statistic analysis
\end{itemize}
\pagebreak

@@

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.25]{GNU-09.jpg}
\caption{Spectral reflectance of seawater with sediments. Bezier interpolation. Mean value is shown by the vertical impulses linestyle (GNUplot)­}
\label{fig:52}
\end{center}
\end{figure}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.25]{GNU-10.jpg}
\caption{Spectral reflectance of the seawater without sediments. Interpolation graph. GNUplot display­}
\label{fig:53}
\end{center}
\end{figure}
\pagebreak

\begin{table}[htbp]
\rowcolors{1}{Ivory}{GhostWhite}
\caption{Summary of the table with values of the spectral reflectance of \textbf{P.oceanica} measured on three different depths, R}
\label{tab:13}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline\hline
wl & X0.5m & X1.5m & X2.5m\\ \hline\hline
Min.   :318.2   &  Min.   :0.00000     &   Min.   : 0.7792     &   Min.   :0.005096  \\ \hline
 1st Qu.:476.9   &  1st Qu.:0.03398    &  1st Qu.:14.4084    &  1st Qu.:0.091878  \\ \hline
 Median :636.1   &   Median :0.10955    &  Median :22.4621   &  Median :0.269328 \\ \hline 
 Mean   :635.6   &   Mean   :0.11392   &   Mean   :19.6899   &  Mean   :0.301121  \\ \hline
 3rd Qu.:794.5   &   3rd Qu.:0.17198   &   3rd Qu.:25.8785    &  3rd Qu.:0.431055 \\ \hline  
 Max.   :950.9     &  Max.   :0.32937    &  Max.   :30.9573   &   Max.   :0.981314  \\ \hline
\end{tabular}
\end{center}
From: DepthData $<$- read.table(file="Three-Depths.dat", sep="", header=T); summary(DepthData)
\end{table}

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.25]{GNU-11.jpg}
\caption{Spectral reflectance of P.oceanica. Measurement series 25-50. GNUplot display­}
\label{fig:54}
\end{center}
\end{figure}
\pagebreak

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.25]{GNU-12.jpg}
\caption{RS reflectance of P.oceanica. Series 1-25. Shown midspread of the statistical quartiles Q1 and Q3 (vertical dashes) and
mean value within the range.­}
\label{fig:55}
\end{center}
\end{figure}

%%% Gretl

\begin{table}[htbp]
\caption{\textit{Two-Stage Least Squares}: results of the \textit{TSLS} analysis of the measurement set 1-191 of the spectral reflectance of \textbf{P.oceanica} (15.X.). Gretl.}
\begin{center}
Model 1: TSLS, using observations 1--191\\
Dependent variable: const\\
Instrumented: v17 \\
Instruments: v12 \\

\vspace{1em}

\begin{tabular}{lr@{.}lr@{.}lr@{.}lr@{.}l}
  &
 \multicolumn{2}{c}{Coefficient} &
  \multicolumn{2}{c}{Std.\ Error} &
   \multicolumn{2}{c}{$z$} &
    \multicolumn{2}{c}{p-value} \\[1ex]
v17 &  6 & 88502 & 0 & 527503 & 13 & 0521 & 0 & 0000 \\
\end{tabular}

\vspace{1ex}
\begin{tabular}{lrlr}
Mean dependent var &  1.000000 & S.D. dependent var &  0.000000 \\
Sum squared resid &  97.51535 & S.E. of regression &  0.716407 \\
Log-likelihood & $-$237.5799 & Akaike criterion &  477.1598 \\
Schwarz criterion &  480.4121 & Hannan--Quinn &  478.4771 \\
\end{tabular}

\vspace{1em}
\begin{raggedright}
Hausman test --\\
\quad Null hypothesis: OLS estimates are consistent\\
\quad Asymptotic test statistic: $\chi^2(1)$ = 13.2834\\
\quad with p-value = 0.000267768\\
\vspace{1ex}
Weak instrument test -- \\
\quad First-stage $F(1, 190)$ = 16670.2 \\
\end{raggedright}

\end{center}
\label{tab:14}
\end{table}
%%% Gretl

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.4]{GNU-14.jpg}
\caption{Multiplot of spectral reflectance of P.oceanica. Series 126-150. Shown midspread of the statistical quartiles Q1 and Q3 (vertical dashes) and
mean value within the range (red bold dots). GNUplot visualization­}
\label{fig:56}
\end{center}
\end{figure}
\pagebreak

\begin{table}[htbp]
\rowcolors{1}{Ivory}{GhostWhite}
\caption{Initial Cluster Centers: results of the \textit{K-means} analysis of the measurement set 201-236 of the spectral reflectance of \textbf{P.oceanica} (15.X.). SPSS}
\label{tab:13}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline\hline
& \multicolumn{2}{|c|}{Cluster} &  & \multicolumn{2}{|c|}{Cluster}\\
%\cline{2,3,5,6}
 & 1 & 2 &  & 1 & 2 \\ \hline\hline
V2 &	.353010 &	.000644 &	V16 &	.240091 &	.000374 \\ \hline
V3 &	 .271519 &	.000394 &	V17 &	.270306 &	.000435 \\ \hline
V4 &	.273594 &	.000644 &	V18 &	.196188 &	.000211 \\ \hline
V5 &	.406525 &	.000527 &	V19 &	.301486 &	.000370 \\ \hline
V6 &	.344973 &	.000509 &	V20 &	.178575 &	.000328 \\ \hline
V7 &	.395117 &	.000646 &	V21 &	.231708 &	.000440 \\ \hline
V8 &	.254642 &	.000352 &	V22 &	.186493 &	.000365 \\ \hline
V9 &	.288881 &	.000267 &	V23 &	.261761 &	.000418 \\ \hline
V10 &	.191850 &	.000255 &	V24 &	.282032 &	.000264 \\ \hline
V11 &	.249462 &	.000323 &	V25 &	.190709 &	.000375 \\ \hline
V12 &	.209622 &	.000414 &	V26 &	.177432 &	.000206 \\ \hline
V13 &	.218312 &	.000206 &	V27 &	.195104 &	.000268 \\ \hline
V14 &	.177432 &	.000268 &	V28 &	.256630 &	.000386 \\ \hline
V15 &	.184836 &	.000223 &	V29 &	.283744 &	.000436 \\ \hline
	 &	 &	 &		V30 &	.406525 &	.000646 \\ \hline
\end{tabular}
\end{center}
\label{tab:14}
\end{table}
